О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
Just a label
The first estimate for a line segment

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta|=l$ and $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = n^2 + 1$.
	Then
	\begin{equation}
		l \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n
		.
	\end{equation}
\end{lemma}

@@

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta| = l$ and $M \in \mathfrak{M}(2,n)$ for some $n>122$.
	Let $\#(\Delta \cap M) = k > 10000$.
	Then $l\geq \gamma_1 k^{3/2}$,
	TODO: why 10 000 ???
	where

	TODO!
\end{lemma}

>>>>

\begin{lemma}
	\label{lem:line_segment_with n_squared_plus_one_points}
	Let $\Delta$ be a straight line segment, $|\Delta|=l$ and $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = n^2 + 1$.
	Then
	\begin{equation}
		l \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n
		.
	\end{equation}
\end{lemma}

@@

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta| = l$ and $M \in \mathfrak{M}(2,n)$.
	Let $\#(\Delta \cap M) = t$.
	Then $l\geq \frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5}{6}t^{1/2}$.
\end{lemma}

\begin{proof}
	Let $f(k)$ denote the mininal length of a line segment
	that shares $k$ points with and integral point set.
	We observe that $f(k) > f (k-1)$.
	Due to Lemma~\ref{lem:line_segment_with n_squared_plus_one_points},
	$f(n^2+1) \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$.

	Consider $t$ such that $n^2 + 1 \leq t \leq (n+1)^2$. %,
	%then $f(t) > f(n^2 +1)$.% and $n \geq \sqrt{t} - 1$.
	For $t\in\mathbb{N}$ the inequality $(\sqrt{t} - 1)^2 +1 \leq t$ holds,
	thus
	%and derive that
	\begin{equation}
		\label{eq:line_segment_length}
		f(t) \geq f((\sqrt{t} - 1)^2 +1) \geq \frac{2}{3}(\sqrt{t} - 1)^3+\frac{1}{2}(\sqrt{t} - 1)^2-\frac{1}{6}(\sqrt{t} - 1)
		=
		\frac{2}{3}t^{3/2}-\frac{3}{2}t+\frac{5 }{6}t^{1/2}
		.
	\end{equation}
\end{proof}
